### 2024-02-25 paper/paper.tex
added initial abstract and intro

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
Citation networks are graphical networks composed of publications as nodes and citations as edges. They offer a unique look into scientific collaboration and the flow of knowledge within academia. In this paper, we examine the history of machine learning hardware papers through the lens of citation networks and construct GNN models for node classification and link prediction for our custom machine learning hardware dataset as well as existing datasets in software engineering and machine learning. We utilize existing citation graphs as well as curate our own dataset from the Web of Science database to show that node classification and link prediction are effective on a new network of machine learning hardware papers.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
Inspired by the recent advent of graphical neural networks (GNNs), this project explores their potential to classify academic networks. Given any individual publication or author, GNNs could predict their relation to the remainder of the network, useful for understanding the relationships between academic fields, authors, institutions, and more. This opens the door to opportunities for classifying papers in fields with minimal representation in existing citation networks or predicting links between papers, potentially applicable to discovering inspiring papers related to an author's past work,  among other capabilities. \par
In particular, machine learning hardware is a new field that has skyrocketed from the recent popularity of machine learning. Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these computing loads. We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the new corpus of machine learning hardware papers. The main challenges are processing data for useful representations of the network and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par
\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-03-10 paper/paper.tex
adapted half of class paper to latex

@@
 
-\begin{IEEEkeywords}
-component, formatting, style, styling, insert
-\end{IEEEkeywords}
+% \begin{IEEEkeywords}
+% component, formatting, style, styling, insert
+% \end{IEEEkeywords}
 
-\section{Introduction}
+\section{Introduction and Motivation}
 Inspired by the recent advent of graphical neural networks (GNNs), this project explores their potential to classify academic networks. 
-Given any individual publication or author, GNNs could predict their relation to the remainder of the network, useful for understanding the relationships between academic fields, authors, institutions, and more.
-This opens the door to opportunities for classifying papers in fields with minimal representation in existing citation networks or predicting links between papers, potentially applicable to discovering inspiring papers related to an author's past work,  among other capabilities.
-\par
+Given any individual publication or author, GNNs could predict their relation to the remainder of the network, 
+useful for understanding the relationships between academic fields, authors, institutions, and more. This opens the door to 
+opportunities for classifying papers in fields with minimal representation in existing citation networks or predicting links 
+between papers, potentially applicable to discovering inspiring papers related to an author's past work, 
+among other capabilities. \par
+
 In particular, machine learning hardware is a new field that has skyrocketed from the recent popularity of machine learning. 
-Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these computing loads.
-We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the new corpus of machine learning hardware papers.
-The main challenges are processing data for useful representations of the network and data interpretation on the created GNNs to comment on the field of machine learning hardware.
-\par
-\section{Ease of Use}
+Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these 
+computing loads. We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the 
+new corpus of machine learning hardware papers. The main challenges are processing data for useful representations of the network 
+and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par
+\section{Previous Work}
+There have been many previous explorations of citation networks using the datasets Cora, Citeseer, and PubMed Diabetes. 
+In these citation networks, in particular, node classification and link prediction have been heavily explored. 
+In Optimization of Graph Neural Networks with Natural Gradient Descent, Izadi et al improve on traditional optimization 
+algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
+by utilizing a proposed method inspired by natural gradient descent [1]. This paper achieved the highest accuracy across 
+71 different papers done on node classification of the Cora dataset.  \par
 
-\subsection{Maintaining the Integrity of the Specifications}
+Those that explored link prediction in the Cora and Citeseer datasets have achieved great results as well. 
+In ‘NESS: Node Embeddings from Static SubGraphs,’ Ucar proposed splitting up the graph into multiple subgraphs 
+that do not have overlapping edges in between subgraphs, using each graph to train and obtain node representations, 
+then aggregating the results to obtain predictions [2]. Using this, he was able to obtain state-of-the-art accuracy results, 
+achieving 98.94±0.1\% on Citeseer and 96.81±0.6\% on Cora. In ‘Neural Link Prediction with Walk Pooling,’ L. 
+Pan et al proposed a GNN architecture that adds attention mechanisms to GNNs, achieving an accuracy of 89.59±1.58\% [3]. 
+These past studies show the efficacy of GNNs on academic publications for node classification and link prediction, and, 
+since these accuracies were certainly impressive, we hope to use these networks as a baseline to examine the key features 
+of different datasets and extract information to create a similar dataset about the subject of machine learning hardware.  \par
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\section{Approach}
 
-\section{Prepare Your Paper Before Styling}
+Two preconstructed datasets, Cora and CiteSeer, are large datasets of scientific machine learning papers. 
+Each dataset contains papers from before 2008, with citations to other papers in the database as well as the 
+vocabulary used. The nodes of the graph are the papers themselves, with topics and vocabulary as individual features, 
+while the directed links are citations to other papers. Cora classifies each publication into one of seven categories: 
+Theory, Reinforcement Learning, Genetic Algorithms, Neural Networks, Probabilistic Methods, Case Based, and Rule Learning. 
+On the other hand, Citeseer classifies each publication into one of six categories: Agents, Artificial Intelligence, Database, 
+Human Computer Interaction, Machine Learning, and Information Retrieval. \par
+
+Meanwhile, PubMed is a database of diabetes publications that is classified into one of three classes [4]. As such, this 
+dataset is similar to both Cora and CiteSeer, though it further explores the efficacy of GNNs on datasets outside of 
+machine learning. This performance of this dataset can further validate parameters potentially affecting accuracies, 
+such as edge count, classes, or path length,  in addition to explaining differences in different fields of publications. \par
+
+Web of Science (WoS) is an online database of publication citations and information [5]. 
+This online database created by Clarivate can be queried by genre and shows identifying information such as titles, 
+references, and specific citations. As such, we can utilize the WoS dataset to address the goal of exploring additional 
+datasets in machine learning hardware. Specifically, by downloading papers by (exclusive) topic, 
+we can create a dataset representative of the field of machine learning and compare the performance of our dataset 
+against GNNs alongside other common datasets to analyze its efficacy on these models and its viability as a dataset 
+in an academic setting. Using this popular database, we query their dataset of publications for four categories: 
+Machine Learning on the Edge, Neuromorphic Computing, Spiking Neural Networks, and Machine Learning Accelerator. 
+In using the Web of Science database, we assume that the papers are representative of their assigned class and 
+distinct from related classes. In this regard, the dataset that we curate is unique from other citation networks 
+in that it will hold distinct characteristics and be of machine learning hardware, providing insight into the 
+structure and nature of the machine learning hardware citation network. \par
+
+Beginning with the provided models like Deep Graph Library, we take inspiration from existing methods, 
+such as preprocessing methods discussed by the Semantic Scholar Academic Graph [6]. By constructing our 
+datasets of publications, we will examine model characteristics of varying types of publication networks. 
+We also explored other datasets to improve the diversity of our datasets. The  Microsoft Open Academic Graph [7], 
+a large academic graph dataset, shows a promising example of dataset scale, though it has differences in 
+features, scaling, and overlapping that can interfere with providing information about any one academic field. 
+Here, the data set uses a variety of data types for the nodes, like publications, authors, and venues, with 
+the links between each denoting a correlation. \par
+
+Following the specified approach to our project goals, the main tasks of our project are as follows. 
+First, we will apply the necessary pre-processing techniques to each dataset for model compatibility. 
+Then, we will create a GNN model using each dataset that accurately predicts paper topics and citations, 
+commenting on the accuracy and effectiveness of GNNs in node classification or link prediction in academic 
+contexts. For node classification, we will create a GNN model based on the vocabulary and neighbors as 
+embeddings of each node, experimenting with different configurations to find the best model. Finally, 
+we will take the results in terms of graph characteristics and model performance to analyze our dataset 
+as an academic tool. In this regard, our technique is rather scalable, as these steps can be applied to 
+academic datasets of nearly any field and in datasets beyond academic publications as well. However, 
+this is also given the assumption that different academic fields follow similar citation networks to 
+those listed, that these fields can be described by the vocabularies that they exhibit, and that 
+these networks produce a graph that is compatible with neural network models. \par
+
+\section{Experimental Setup and Results}
+
+\subsection{Datasets}
+
+Since the datasets Cora and Citeseer are included within some deep learning packages, 
+we directly use those for constructing GNNs. Utilizing resources and configurations of 
+included models within StellarGraph, Pytorch Geometric, and Keras, we can also construct 
+predictive models for node classification and link prediction. \par
+
+In creating our dataset, we query Web of Science for topics in machine learning 
+hardware published between 1970 and 2022. For ease of use, we removed nodes without a 
+DOI and duplicated values between categories so each node only belongs to one category. 
+The collected data includes title, publishing year, abstract, and citations. \par
+
+While Web of Science shows a close-to-linear growth of publications during this time, 
+there has been an exponential growth of papers in machine learning hardware over the 
+same period. We see a large spike in interest, following machine learning in general 
+after OpenAI launched GPT. \par
+
+With the text files generated, we constructed a NetworkX graph using DOI values to 
+match paper citations. We also utilized the categories as labels, and the overall 
+graph topography is in Figure A. This graph serves as our dataset once converted 
+into StellarGraph or NetworkX Pytorch Geometric dataset instances as needed. \par
+
+In total, our graph had 4951 nodes, though only 2605 nodes have non-zero edges. 
+Looking at the in-degrees of each node, we see evidence of a scale-free network, 
+where few nodes are popularly cited, but many are not referenced often. This may 
+also be due to the recentness of these publications, as future papers will likely 
+add on to those numbers. The number of paper citations is also indicative of its 
+impact, with larger in-degrees meaning more outreach and influence. \par
+
+Removing nodes without edges allows us to focus on the variety in edges and prevents 
+the model from predicting 0 edges each time for high accuracy, the resulting is 
+still disconnected, with an average degree of 5.0672, an average clustering coefficient 
+of 0.1353, and a maximum diameter across all connected subgraphs of 16, 
+with the average undirected path length being 4.6073 edges. \par
+
+However, from observation, we notice that our graph is much smaller and less connected 
+than the given datasets. As in Figure 1 below, there are lots of unconnected nodes. 
+And, after removing non-zero edges, there are still plenty of nodes that have only 
+one edge to another paper, likely due to their remaining citations not having an associated 
+word vector. \par
+
+To combat this, we increase the size of the WoS database, querying additional nodes from the 
+WoS database. Then, we take the largest connected component of the 
+larger graph to increase the overall connectivity of the graph. \par
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.3] {wos_pic.png}}
+    \caption{Large WoS network, Blue=ML Accelerators, Purple=Edge ML, Green=Neuromorphic Computing, Orange=Spiking Neural Network.}
+    \label{fig}
+\end{figure}
+
 Before you begin to format your paper, first write and save the content as a 

### 2024-03-11 paper/paper.tex
added more paragraphs, created a table in latex

@@
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
+\title{Conference Paper Title\\
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 They offer a unique look into scientific collaboration and the flow of knowledge within academia. 
-In this paper, we examine the history of machine learning hardware papers through the lens of citation networks and construct GNN models for node classification and link prediction for our custom machine learning hardware dataset as well as existing datasets in software engineering and machine learning.
-We utilize existing citation graphs as well as curate our own dataset from the Web of Science database to show that node classification and link prediction are effective on a new network of machine learning hardware papers.
+In this paper, we examine the history of machine learning hardware papers through the lens of citation 
+networks and construct GNN models for node classification and link prediction for our custom machine 
+learning hardware dataset as well as existing datasets in software engineering and machine learning. 
+We utilize existing citation graphs as well as curate our own dataset from the Web of Science database 
+to show that node classification and link prediction are effective on a new network of machine learning 
+hardware papers.
 \end{abstract}
@@
 and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par
+
 \section{Previous Work}
@@
 \end{figure}
+
+After applying these operations, the total number of nodes increases from 2,605 to 9,605 after removing 
+unusable nodes. This graph also has 52,945 edges and 6,821 features, from applying the 
+same methods of keyword extraction. When increasing the size of the dataset, we were also 
+met with a class imbalance - there were far fewer papers in ML Accelerators in the WoS database, 
+less than two thousand papers, while the other categories had over five thousand papers each. 
+In this regard, we can infer that ML accelerators are less popular (or at least less explored) 
+than other papers. However, since WoS is our only source of data, this could also result from 
+a lack of these papers in the Web of Science database. Since class imbalances can also impact 
+performance on ML models, this also acts as a limitation on the GNN models in use. \par
+
+Recognizing that the number of features is nearly double that of any of the given datasets, 
+this can also lead to excessive computation time and increased bias in the results from 
+features that supply noise in the machine learning models. So, we then apply principal 
+component analysis (PCA) to these features to select the features that best describe the 
+classifications and links between each node. Here, we apply PCA with an explained variance 
+of 80\% to provide a sufficient level of specificity without overfitting the data, 
+reducing the number of features to 760. \par
+
+Following this, we also update the characteristics of our graph, producing an average 
+degree of 11.09, an average clustering coefficient of 0.158, and a diameter of 18. 
+From the differences in these datasets, we see that the average degree of our dataset 
+is much higher than the given datasets. However, the clustering coefficient and diameter 
+of the dataset are comparable to those of other datasets. These metrics are compared to 
+the other datasets in Table 1 below. \par
+
+From this table, we can see differences among the datasets explored in this paper, 
+revealing the structural properties of these different graphs. Primarily, there are 
+many more edges in the updated WoS compared to the other datasets, resulting in a much 
+higher average degree for the updated dataset. However, the clustering coefficient for 
+our dataset is still comparable to other datasets, implying that the field of machine 
+learning hardware tends to have a significant number of citations, but a similar number 
+of these papers forming a well-defined cluster. While Cora and CiteSeer are most similar 
+to the WoS database in terms of content, both relating to machine learning, the graph 
+characteristics of WoS are most similar to PubMed, with a higher degree and lower 
+clustering coefficient. However, another limitation of utilizing WoS as our primary 
+database is that it is unclear whether these characteristics arise as a quality of 
+the database or as a characteristic of the field of ML hardware in general. \par
+
+\begin{table}[htbp]
+    \caption{Citation Network Characteristics}
+    \begin{center}
+        \begin{tabular}{|c|cccccc|}
+        \hline
+        % \textbf{Table}&\multicolumn{6}{|c|}{\textbf{Table Column Head}} \\
+        % \cline{1-4} 
+        \textbf{} & \textbf{\textit{Nodes}} & \textbf{\textit{Edges}} & \textbf{\textit{Features}} &
+        \textbf{\textit{Degree}} & \textbf{\textit{CC$^{\mathrm{a}}$}} & \textbf{\textit{MD$^{\mathrm{b}}$}} \\
+        \hline
+        \textbf{\textit{Cora}} & 
+        2708& 5429& 1433& 3.89807& 0.24067& 19 \\
+        \textbf{\textit{CiteSeer}} & 
+        3312& 4660& 3704& 2.81400& 0.14255& 28 \\
+        \textbf{\textit{Pubmed}} & 
+        19717& 44348& 500& 4.49632& 0.06017& 18 \\
+        \textbf{\textit{Small WoS}} & 
+        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
+        \textbf{\textit{Large WoS}} & 
+        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
+        \hline
+        \end{tabular}
+        \label{tab1}
+        {$^{\mathrm{a}}$Clustering Coefficient.}
+        {$^{\mathrm{b}}$Maximum Diameter.}
+    \end{center}
+\end{table}
 

### 2024-03-11 paper/paper.tex
added more figures, paragraphs

@@
 
+To see the distribution of the demographic of the papers in terms of age, 
+we look at the number of papers in our updated WoS database, as in Figure 2 
+below. From this graph, we see that papers have been released more frequently 
+in recent years. This implies that machine learning hardware is a rising field, 
+which follows given the recent popularity of machine learning as a field in general. \par
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.3] {papers_by_year.png}}
+    \caption{Growth of Papers Published in ML Hardware over Time.}
+    \label{fig}
+\end{figure}
+
+After applying these changes, we define a t-SNE visualization on the dataset, 
+as pictured in Figure 3. The plot helps to establish underlying patterns and 
+relationships in the dataset on a 2-D plane for reader understandability. 
+From this plot, we see that there are some strong clusters of papers and 
+some much weaker, though still characteristic. \par
+
+Then, after finding the edge list of the dataset, we can plot the degree distribution 
+chart of the network, plotting the number of times a paper was cited against the 
+frequency of that number of citations, shown in Figure 5 below. \par
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.3] {tsne_embeddings.png}}
+    \caption{t-SNE Plot of the WoS Dataset.}
+    \label{fig}
+\end{figure}
+
+From this plot, we establish that the WoS citation network shows 
+characteristics of a small-world network, with few nodes exhibiting 
+a high number of citations and most having very few citations. 
+This result makes sense, as few papers are likely to have a high 
+impact, and those that do are likely to influence many papers. \par
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[scale=0.3] {times_cited.png}}
+    \caption{Occurrences for papers with certain times cited.}
+    \label{fig}
+\end{figure}
+
+Looking at the most-cited nodes, we find impactful key publications 
+in their respective fields. One such publication is “Equivalent-accuracy 
+accelerated neural-network training using analogue memory”, published in 2016 [7]. 
+In “Nanoscale memristor device as synapse in neuromorphic systems'' published 
+in 2018,  Jo et al. experimentally show a nanoscale memristor working within 
+the context of neuromorphic computing [8]. In another example, “Memory devices 
+and applications for in-memory computing” gives an overview of potential solutions 
+to in-memory computing, including solutions closely related to machine learning and 
+digital signal processing [9]. \par
+
+In finding additional outliers, we were also able to distinguish the age of our papers. 
+The dataset consisted of papers from the years of 1971 to 2023. Since machine 
+learning was identified as a rising field from the discussion regarding Figure 2, 
+there were many papers from 2023. And, since many papers only provided a month as 
+the date of publication, the multiple papers from November of 2023 prevented the 
+identification of the newest paper. However, the oldest paper, the only paper from 
+1971, was titled “Unit Spike Activity in Coelenteran Neural Network”, a paper about 
+temperature spikes in primitive neural nerve networks [10]. \par
+
+While both Cora and Citeseer categorize publications and have vocab dictionaries, 
+there are no such categories or dictionaries for Web of Science results. 
+Therefore, we utilized the search function to specify the categories to be 
+both used and excluded in each search. To match the vocabularies of Cora and 
+Citeseer, we utilized spacy for trained keyword extraction models, finding 
+the top 10 unigrams with the most significance in each abstract, and used 
+these words to construct our vocabulary vectors [11].
+
 Before you begin to format your paper, first write and save the content as a 

### 2024-03-11 paper/paper.tex
halfway on 2x2 figures, started bib

@@
 \usepackage{xcolor}
+% mine own
+\usepackage{caption}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
-by utilizing a proposed method inspired by natural gradient descent [1]. This paper achieved the highest accuracy across 
-71 different papers done on node classification of the Cora dataset.  \par
+by utilizing a proposed method inspired by natural gradient descent. This paper achieved the highest accuracy across 
+71 different papers done on node classification of the Cora dataset \cite{CoraAccuracy}.  \par
 
@@
 that do not have overlapping edges in between subgraphs, using each graph to train and obtain node representations, 
-then aggregating the results to obtain predictions [2]. Using this, he was able to obtain state-of-the-art accuracy results, 
-achieving 98.94±0.1\% on Citeseer and 96.81±0.6\% on Cora. In ‘Neural Link Prediction with Walk Pooling,’ L. 
-Pan et al proposed a GNN architecture that adds attention mechanisms to GNNs, achieving an accuracy of 89.59±1.58\% [3]. 
+then aggregating the results to obtain predictions. Using this, he was able to obtain state-of-the-art accuracy results, 
+achieving 98.94±0.1\% on Citeseer and 96.81±0.6\% on Cora. \cite{Ucar}
 These past studies show the efficacy of GNNs on academic publications for node classification and link prediction, and, 
@@
 
-Meanwhile, PubMed is a database of diabetes publications that is classified into one of three classes [4]. As such, this 
+Meanwhile, PubMed is a database of diabetes publications that is classified into one of three classes \cite{Pubmed}. As such, this 
 dataset is similar to both Cora and CiteSeer, though it further explores the efficacy of GNNs on datasets outside of 
@@
 
-Web of Science (WoS) is an online database of publication citations and information [5]. 
+Web of Science (WoS) is an online database of publication citations and information \cite{WoS}. 
 This online database created by Clarivate can be queried by genre and shows identifying information such as titles, 
@@
 Beginning with the provided models like Deep Graph Library, we take inspiration from existing methods, 
-such as preprocessing methods discussed by the Semantic Scholar Academic Graph [6]. By constructing our 
+such as preprocessing methods discussed by the Semantic Scholar Academic Graph \cite{Wade}. By constructing our 
 datasets of publications, we will examine model characteristics of varying types of publication networks. 
-We also explored other datasets to improve the diversity of our datasets. The  Microsoft Open Academic Graph [7], 
+We also explored other datasets to improve the diversity of our datasets. The  Microsoft Open Academic Graph \cite{Sinha}, 
 a large academic graph dataset, shows a promising example of dataset scale, though it has differences in 
@@
         \hline
-        % \textbf{Table}&\multicolumn{6}{|c|}{\textbf{Table Column Head}} \\
-        % \cline{1-4} 
         \textbf{} & \textbf{\textit{Nodes}} & \textbf{\textit{Edges}} & \textbf{\textit{Features}} &
@@
 the top 10 unigrams with the most significance in each abstract, and used 
-these words to construct our vocabulary vectors [11].
+these words to construct our vocabulary vectors [11]. \par
+
+\begin{figure}[htbp]
+    % \centering
+    \caption{Number of Papers per Year by Category}
+    \captionsetup{labelformat=empty}
+    \parbox[b]{.5\linewidth}{
+    \includegraphics[scale=0.23]{papers_by_year.png}
+    \caption{A cat}\label{cat}}
+    \parbox[b]{.45\linewidth}{
+    \includegraphics[scale=0.23]{times_cited.png}
+    \caption{An elephant}\label{elephant}}
+%   \caption{Number of Papers per Year by Category}\label{animals}
+    \captionsetup{labelformat=simple}
+\end{figure}
+
+In Table 1, we examine the structure of each community by computing the mixed 
+edge probability, i.e. how many out of the total edges in the graph contain 
+an edge from one community to other communities. The mixed edge theoretical 
+probability of a certain category, say A, is the probability that any node 
+is in A out of all nodes, multiplied by the probability that any node is 
+in any other category. We use this simple equation: \par
+
+% TODO: fix new line problem!
+\begin{equation}
+    Theoretical\; Mixed\; Edge\; Probability(category\; A)
+    \\
+    = (P(node\; in\;A)) (1 - P(node\;in\;A))\label{eq}
+\end{equation}
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{CoraAccuracy} "Node Classification on Cora", url: https://paperswithcode.com/sota/node-classification-on-cora.
+\bibitem{Ucar} T. Ucar, "NESS: Node Embeddings from Static SubGraphs", in arXiv, 2023, url: https://doi.org/10.48550/arXiv.2303.08958. 
+\bibitem{Pubmed} National Library of Medicine, "Pubmed", url: https://relational.fit.cvut.cz/dataset/PubMed\_Diabetes.
+\bibitem{WoS} Clarivate, "Web of Science", 2023, url: https://www.webofscience.com/wos/woscc/basic-search.
+\bibitem{Wade} A. D. Wade, "The semantic scholar academic graph (s2ag)", in Companion Proceedings of the Web Conference 2022, 2022, pp. 739-739.
+\bibitem{Sinha} A. Sinha et al., "An overview of microsoft academic service (mas) and applications", in Proceedings of the 24th international conference on world wide web, 2015, pp. 243-246.
+\bibitem{Ambrogio} S. Ambrogio et al., "Equivalent-accuracy accelerated neural-network training using analogue memory", Nature, vol. 558, no. 7708, pp. 60-67, 2018.
 \end{thebibliography}

### 2024-03-11 paper/paper.tex
prelim fix of tables, added conclusion

@@
 % mine own
-\usepackage{caption}
+% \usepackage{caption}
+\usepackage{tabularx}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{Conference Paper Title\\
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{Collaborative Networks in Machine Learning Hardware\\
+\thanks{University of Texas at Austin}
 }
@@
 In finding additional outliers, we were also able to distinguish the age of our papers. 
-The dataset consisted of papers from the years of 1971 to 2023. Since machine 
-learning was identified as a rising field from the discussion regarding Figure 2, 
-there were many papers from 2023. And, since many papers only provided a month as 
-the date of publication, the multiple papers from November of 2023 prevented the 
-identification of the newest paper. However, the oldest paper, the only paper from 
-1971, was titled “Unit Spike Activity in Coelenteran Neural Network”, a paper about 
-temperature spikes in primitive neural nerve networks [10]. \par
+The dataset consisted of papers from the years of 1971 to 2023. The oldest paper, 
+the only paper from 1971, was titled “Unit Spike Activity in Coelenteran Neural Network”, 
+a paper about temperature spikes in primitive neural nerve networks [10].  \par
 
@@
 \begin{figure}[htbp]
-    % \centering
+    \centering
     \caption{Number of Papers per Year by Category}
-    \captionsetup{labelformat=empty}
+    % \captionsetup{labelformat=empty}
     \parbox[b]{.5\linewidth}{
@@
     \caption{An elephant}\label{elephant}}
-%   \caption{Number of Papers per Year by Category}\label{animals}
-    \captionsetup{labelformat=simple}
+    \hfill
+    \parbox[b]{.5\linewidth}{
+    \includegraphics[scale=0.23]{papers_by_year.png}
+    \caption{A cat}\label{cat}}
+    \parbox[b]{.45\linewidth}{
+    \includegraphics[scale=0.23]{times_cited.png}
+    \caption{An elephant}\label{elephant}}
+    % \captionsetup{labelformat=simple}
 \end{figure}
 
-In Table 1, we examine the structure of each community by computing the mixed 
-edge probability, i.e. how many out of the total edges in the graph contain 
-an edge from one community to other communities. The mixed edge theoretical 
-probability of a certain category, say A, is the probability that any node 
-is in A out of all nodes, multiplied by the probability that any node is 
-in any other category. We use this simple equation: \par
+Next, we examine the structure of each community by computing the mixed edge 
+probability, i.e. how many out of the total edges in the graph contain an edge 
+from one community to other communities. The mixed edge theoretical probability 
+of a certain category, say A, is the probability that any node is in A out of 
+all nodes, multiplied by the probability that any node is in any other category. 
+We use this simple equation: \par
 
@@
     Theoretical\; Mixed\; Edge\; Probability(category\; A)
-    \\
-    = (P(node\; in\;A)) (1 - P(node\;in\;A))\label{eq}
 \end{equation}
+\begin{equation}
+    = (P(node\; in\;A)) (1 - P(node\;in\;A))\label{eq1}
+\end{equation}
+
+This number indicates the portion out of all edges that should contain an edge stretching 
+from a node in A to a node outside of A if the graph picked edges at random. \par
+
+Our actual mixed edge probability is calculated by: \par
+\begin{equation}
+    \dfrac{Number\; of\; in\; or\; out\; edges\; of\; a\; community}{Number\; of\; total\; edges}
+    \label{eq2}
+\end{equation}
+
+As seen in Table 2 below, our actual mixed edge probability is far 
+below the theoretical probability in a random graph. \par
+
+% Todo: fix new line problem!
+\begin{table}[htbp]
+    \caption{Mixed Edge Categorical Analysis}
+    \begin{center}
+        \begin{tabular}{|c|cccc|}
+        \hline
+        \textbf{Categories} & \textbf{\textit{Edge}} & \textbf{\textit{ML}} & 
+        \textbf{\textit{Neuromorphic}} & \textbf{\textit{Spiking}} \\
+        \textbf{} & \textbf{\textit{ML}} & \textbf{\textit{Accelerator}} & 
+        \textbf{\textit{Computing}} & \textbf{\textit{NN}} \\
+        \hline
+        \textbf{\textit{Theoretical}} &\ &\ &\ &\ \\
+        \textbf{\textit{Mixed Edge}} &
+        0.19813& 0.19256& 0.19051& 0.16663 \\
+        \textbf{\textit{Probability}} & \ &\ &\ &\ \\
+        \ & \ &\ &\ &\ \\
+        \textbf{\textit{Mixed Edge}} & 
+        0.02101& 0.06806& 0.09880& 0.05195 \\
+        \textbf{\textit{Probability}} & \ &\ &\ &\ \\
+        \hline
+        \end{tabular}
+        \label{tab2}
+    \end{center}
+\end{table}
+
+% TODO: can be removed later
+\ \newline
+\ \newline
+\ \newline
+\ \newline
+\ \newline
+\ \newline
+
+There are far fewer edges in between different categories than edges within a category. 
+As such, these topics within machine learning are distinct subject areas. \par
+
+\subsection{GNNs}
+
+For our baseline, we used a basic five-layer neural network that is essentially trained on word 
+vectors. On Cora, this achieved a 79.43\% accuracy for node classification; 
+on Citeseer, this achieved a 71.43\% accuracy. We then implemented a graphical 
+convolution network model on the Cora dataset with five feed-forward layers, which 
+achieves an accuracy of 71.13\% for link prediction and an accuracy of  86.58\% for 
+node classification. For the CiteSeer dataset, we received an accuracy of 74.1
+\% on node classification and 84.29\% on link prediction. Similarly, the PubMed dataset 
+yielded an accuracy of 78.7\% for both node classification and link prediction. 
+These results were further verified through applying a GNN model from DGL, which received 
+similar results to the previously mentioned models. This makes sense since Cora is a dataset 
+of machine learning papers while CiteSeer has software engineering papers, which is a larger 
+domain. Thus, citations are easier to predict in Citeseer. Furthermore, since Citeseer 
+has as many keywords as they do papers, and there are half as many keywords in Cora, 
+it is more likely that testing on Cora is done on keywords that the model has seen 
+before and is thus more accurate. \par
+
+In this regard, these datasets helped to establish a baseline for the expected performance 
+of a GNN on the dataset created from the Web of Science after PCA. Following similar methods as 
+before, the GNN model for node classification produced an accuracy of 78.06\%, 
+while Link prediction fared much better with an accuracy of 82.56\%. 
+These results are summarized in Table 3 below. \par
+
+\begin{table}[htbp]
+    \caption{GNN Performance Across Datasets}
+    \begin{center}
+        \begin{tabular}{|c|cccccc|}
+        \hline
+        \textbf{Dataset} & \textbf{\textit{Cora}} & \textbf{\textit{CS$^{\mathrm{a}}$}} & \textbf{\textit{PM$^{\mathrm{b}}$}} &
+        \textbf{\textit{WoS1$^{\mathrm{c}}$}} & \textbf{WoS2$^{\mathrm{d}}$} & \textbf{WoS3$^{\mathrm{e}}$} \\
+        \hline
+        \textbf{\textit{Node}} &\ &\ &\ &\ &\ &\ \\
+        \textbf{\textit{Classif-}} &
+        86.58\%& 74.1\%& 78.7\%& 72.3\%& 76.96\%& 78.06\% \\
+        \textbf{\textit{ication}} &\ &\ &\ &\ &\ &\ \\
+
+        \ &\ &\ &\ &\ &\ &\ \\
+
+        \textbf{\textit{Link}} &\ &\ &\ &\ &\ &\ \\
+        \textbf{\textit{Predic-}} &
+        71.13\%& 84.29\%& 78.74\%& 80.8\%& 81.77\%& 82.56\% \\
+        \textbf{\textit{tion}} &\ &\ &\ &\ &\ &\ \\
+
+        \hline
+        \end{tabular}
+        \label{tab1}
+        {$^{\mathrm{a}}$CiteSeer.}
+        {$^{\mathrm{b}}$PubMed.}
+        {$^{\mathrm{c}}$Small WoS.}
+        {$^{\mathrm{d}}$Large WoS.}
+        {$^{\mathrm{e}}$Large WoS w/ PCA.}
+    \end{center}
+\end{table}
+
+From the results in the table, we see that our dataset performs weaker than 
+PubMed and Cora in terms of node classification and weaker than CiteSeer in 
+terms of link prediction. Despite this, our model has the strongest performance 
+averaged between node classification and link prediction, even before PCA. It is 
+also interesting to note that the larger networks in terms of nodes have a smaller 
+difference between the performance of node classification and link prediction, 
+WoS by just a few percentage points and PubMed by less than a tenth of a percent. 
+Similarly, CiteSeer has the lowest average degree and also performs the 
+best for link prediction. \par
+
+However, one of the strongest limitations in the results of the applied models 
+is the lack of knowledge of the cause of performance. The performance of the 
+models could be motivated by differences in the structure of the networks due 
+to the nature of the associated fields, differences in the databases used to 
+curate the networks, and differences in the characteristics of the networks 
+themselves. For example, CiteSeer has multiple self-loops, while the other 
+networks have few if any. Similarly, Cora and CiteSeer are unconnected, while 
+PubMed is connected. Future research on this paper could extend this study to 
+homogenize the datasets by removing self-loops, making all graphs connected, 
+and applying PCA to all datasets to observe any changes in performance. \par
+
+Similarly, a limitation in our approach exists in our dataset in the class 
+imbalance of the ML Accelerator class having far fewer papers than the other 
+classes. This limitation can influence the results of the dataset, such as 
+creating a tendency to not classify a node as ML Accelerator since it is 
+less likely for a paper to belong to this class. This issue can be addressed 
+through solutions such as minority oversampling, creating artificial samples 
+of the ML Accelerator class, or majority undersampling, omitting some samples 
+of the remaining classes to simulate more balanced classes. However, to 
+preserve any information about the underlying structure of the field of 
+ML hardware, we assume that this imbalance of classes is a property of 
+the field of ML hardware, avoiding any manipulation of the original 
+set of samples. \par
+
+For future plans, the most straightforward path is exploring the use of the 
+dataset as an academic tool. Cora and CiteSeer are both extensively used as a 
+tool for the exploration of machine learning, aiming for the strongest results 
+of classification for the dataset. A similar approach can be used for the new 
+WoS dataset, observing the results of these high-performing methods in Cora 
+or CiteSeer on the WoS dataset. Similarly, this dataset can be used to explore 
+new models for classifying or predicting citation networks. Since this dataset 
+has different characteristics than all of the others, it may offer insight 
+into using new or different models than before. \par
+
+Additionally, the models trained on the WoS dataset can be used for node 
+classification or link prediction in a practical sense. By classifying 
+papers in the field of machine learning hardware, the model can help 
+differentiate papers of the two categories in real life. This also 
+applies to link prediction - predicting links on an unpublished paper or 
+abstract can provide insight into potential inspiration from other academic 
+works. Similar applications of link prediction can assist in finding not only 
+papers for inspiration, but also other authors to collaborate with if, 
+for example, both authors have similar published papers. \par
+
+\section{Conclusion and Future Work}
+
+Overall, we reached our goals for this project of developing a new dataset 
+for papers relating to machine learning hardware for a better understanding 
+of the relationships between publications and authors. Through creating a 
+dataset that is well explained through node classification and link prediction, 
+these results can be reproduced for alternative applications like publication 
+classification or potential author collaboration. \par
+
+In the development of this project, we have had the opportunity to witness 
+the application of GNNs on citation networks, in addition to a new dataset. 
+So, we have learned of various qualities of citation networks such as their 
+degree distribution, clustering coefficient, and their underlying network 
+structure, witnessing underlying paper data distribution. We also explore 
+GNN model differences between node classification and link prediction. 
+Creating a new dataset, we saw that GNNs are effective for node classification 
+and link prediction on a new network of machine learning hardware papers. \par
+
+Thus far, we created a dataset of machine learning hardware papers across 
+different demographics with classifications to be used in node classification 
+and link prediction, quantified in terms of characteristics like degree and 
+clustering coefficient, comparing the datasets in terms of traits and GNN performance. 
+While the creation of a competing academic dataset is a strong start to our goal, 
+our created graph still has opportunities for improvement. \par
 

### 2024-03-11 paper/paper.tex
initial pdf of paper

@@
 in 2018,  Jo et al. experimentally show a nanoscale memristor working within 
-the context of neuromorphic computing [8]. In another example, “Memory devices 
+the context of neuromorphic computing \cite{Jo}. In another example, “Memory devices 
 and applications for in-memory computing” gives an overview of potential solutions 
 to in-memory computing, including solutions closely related to machine learning and 
-digital signal processing [9]. \par
+digital signal processing \cite{Sebastian}. \par
 
@@
 the only paper from 1971, was titled “Unit Spike Activity in Coelenteran Neural Network”, 
-a paper about temperature spikes in primitive neural nerve networks [10].  \par
+a paper about temperature spikes in primitive neural nerve networks \cite{Rm}.  \par
 
@@
 the top 10 unigrams with the most significance in each abstract, and used 
-these words to construct our vocabulary vectors [11]. \par
+these words to construct our vocabulary vectors \cite{keywordspacy}. \par
 
@@
 \ \newline
-\ \newline
-\ \newline
-\ \newline
-\ \newline
+% \ \newline
+% \ \newline
+% \ \newline
+% \ \newline
 
@@
 
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
 \begin{thebibliography}{00}
@@
 \bibitem{Ambrogio} S. Ambrogio et al., "Equivalent-accuracy accelerated neural-network training using analogue memory", Nature, vol. 558, no. 7708, pp. 60-67, 2018.
+\bibitem{Jo} Jo SH, Chang T, Ebong I, Bhadviya BB, Mazumder P, Lu W. "Nanoscale memristor device as synapse in neuromorphic systems," in Nano Lett., 10(4):1297-301, 2010, doi: 10.1021/nl904092h.
+\bibitem{Sebastian} A.
+Sebastian, M.
+Le Gallo, R.
+Khaddam-Aljameh, and E.
+Eleftheriou, "Memory devices and applications for in-memory computing", Nature nanotechnology, vol.
+15, no.
+7, pp.
+529-544, 2020.
+\bibitem{Rm} B. Rm, "Unit Spike Activity in Coelenteran Neural Network", NATURWISSENSCHAFTEN, vol. 58, no. 3. Springer Verlag 175 Fifth Ave., New York, NY 10010, p. 153, 1971.
+\bibitem{keywordspacy} Honnibal, M.
+\& Montani, I., keyword-spaCy, Natural language understanding with Bloom embeddings, convolutional neural networks and incremental parsing, 2017, url: https://github.com/wjbmattingly/keyword-spacy.
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}
